---
title: "Vikas Singh's Resume"
author: Vikas Singh 
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: false
# uncomment this line to produce HTML and PDF in RStudio:
knit: pagedown::chrome_print
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)
library(ggplot2)
library(plotly)
library(datadrivencv)
library(tidyverse)
library(dplyr)
library(glue)
library(magrittr) # For the pipe
```
Aside
================================================================================

Contact Info {#contact}
--------------------------------------------------------------------------------
- <i class="fa fa-home"></i> 287 Rue d'Alco, 34080 Montpellier, France, 34080 Montpellier
- <i class="fa fa-envelope"></i> v.vikas@montpellier-bs.com
- <i class="fa fa-github"></i> [github.com/vikass14](https://github.com/vikass14)
- <i class="fa fa-phone"></i> +33 075-413-2021
- <i class ="fa fa-linkedin"></i>("https://www.linkedin.com/in/vikas-singh-8323455a/")


Soft Skills {#soft}
-------------------------------------------------------------------------------
Scientific 
Innovator 
Practical
Organizational 
Conciliator


Research Skills {#skills}
--------------------------------------------------------------------------------
### Qualititative Research Approach
- Grounded Theory
- Phenomenological Research

### Qualitative Research Methods
- Secondary Research
- Interview

### Quantitative Research Approach
- Descriptive
- Causal
- Correlational research


Main
================================================================================

Vikas Singh {#title}
--------------------------------------------------------------------------------

### Currently searching for a Position of Data Analyst(Intern)

I am passionate researcher with strong intuitive skills. Currently pursuing my MSc (Big Data and AI for Business) from Montpellier Business School. I am looking for the position of Data Analyst where I can analyzed and visualize  large data sets for delivering solution to the business problem with use of statistical and machine learning techniques using R, Python and STATA.


Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

### Montpellier Business School

MSc in Big Data and Artificial Intelligence for Business

Montpellier,France

Jan,2023-Current

### National Institute of Food Technology Entrepreneurship and Management

PhD Food Business Management

Kundli,India

Aug,2013-Feb,2019

Thesis:Structure of Microfinance Institutions and their impact on the Performance of Self-Help Groups: An Empirical Study

### University School of Management, Kurukshetra University

MBA

Kurukshetra,India

May,2007-Jun,2009

Project: Debt Refinancing Scheme of Power Finance Corporation, India 

### University of Delhi

BSc 

New Delhi,India

May,2003-Jun,2009

Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

### Consultant (Data Analyst cum Monitoring & Evaluation Officer)

Department of Food and Public Distribution System, Ministry of Consumer Affairs, GoI

New Delhi,India

Aug,2021-Dec,2022

- Devise strategic monitoring and evaluation plans for all schemes Department of Food and Public Distribution(DoFPD).
- Performed various analysis Including; Descriptive, Predictive, Causal, Infrential  using, R and Python for 12 schemes of the DoFPD.
- Developed a time series forecasting model using ARIMA and SARIMA to forecast  procurement and distribution for  DoFPD.
- Developed indicators based on Output Outcome Framework (OOMF)for monitoring different schemes.-
- Build Chatbot using Tensorflow and nltk package in Python.
- Produce maps showing the spatial distribution of ethanol production data using Python.
- Mentored and guide young professionals

### Health Data Analyst

All India Institute of Medical Sciences

Rishikesh, India

Oct,2020-Dec,2016

- Extract 40,000 observation of national sample survey (NSS) 75th round data using STATA and R.
- Conduct survival analysis  using R.
- Summarized , analyzed socio-economic data and performed logistics regression, t-test, Chi-square , cross-tabulation , ANOVA in R.

::: aside
**PROGRAMMING SKILLS**

```{r ,fig.width=30,fig.height=30}
dataC <- data.frame(
  Tools = c("R","Python","Linux", "SQL","Pandas", "Numpy", "ggplot2","plotly",
            "matplotlib","scikit-learn", "TensorFlow","Rshiny"),
  Skills = c("Programming","Programming","Programming", "Data processing & wrangling",
             "Data processing/wrangling", "Data processing & wrangling",
             "Data visualization", "Data visualization", "Data visualization",
             "Machine Learning", "Deep Learning", "Model deployment"),
  Levels = c(4,3.5,2,3,4,2,5,5,3,3,3,4)
)
ggplot(dataC, aes(x = Tools, y = Levels, fill = Tools)) +
  geom_bar(stat = "Identity")+ylim(0,5)+coord_flip()+theme(text = element_text(size = 80))+ theme(legend.position = "none")
```
:::

### Research Associate

National Institute of Food Technology Entrepreneurship and Management

Kundli, India

Oct,2019-Oct,2020

- Design and developed survey tool for social entrepreneurship impact assessment in Rshiny.
- Identfy KPIs using bibliometrics analysis in rstudio.
- Performed exploratory data analysis and write scientific research articles in journals


### Assistant Professor (Ad-Hoc)

Cluster Innovation Centre, University of Delhi

New Delhi,India

Sep,2017-May,2019

- Taught 15+ undergraduate/graduate classes on financial management, macroeconomics,marketing and Use for R in finance.
- Provided mentorship and supervision to B.Tech. students.

### Research Associate

Indian Institute of Foreign Trade

New Delhi,India

May,2017-Jul,2019

- Collect and analyzed data on international trade, economic, and other regional trends of textile sector.
- Write reports, policy updates, and issue briefs using quantitative analysis that explained data trends.

::: aside
**STATISTICAL SKILLS**

```{r,fig.width=10,fig.height=10}
library(fmsb)
# Create data: note in High school for Jonathan:
data2 <- data.frame(
  row.names = c("Score"),
  "Ordered L Reg" = 5,
  "MANOVA" = 5,
  "PCA" = 5,
  "MCA" = 5,
  "Probit Reg" = 4,
  "ARIMA" = 5,
  "GARCH" = 4,
  "Correlation" = 5,
  "ANFIS" = 5,
  "K-mean Clustering" = 5,
  "SVM" = 3,
  "Factor Analysis" = 5)
df1 <- data.frame(
  "Ordered L Reg" = c(5,0), "MANOVA" = c(5,0), "PCA" = c(5,0), "MCA" = c(5,0),
  "Probit Reg" = c(5,0), "ARIMA" = c(5,0), "GARCH" = c(5,0), "Correlation" = c(5,0), "ANFIS" = c(5,0), "K-mean Clustering" = c(5,0), 
  "SVM" = c(5,0),"Factor Analysis" = c(5,0))

# Bind the variable ranges to the data
rownames(df1) <- c("Max", "Min")
# Bind the variable ranges to the data
df2 <- rbind(df1,data2)
Level2 <- df2[c("Max", "Min", "Score"), ]
rdata1 <- df2[c("Max", "Min", "Score"), ]
create_beautiful_radarchart <- function(data2, color = "#00AFBB", 
                                        vlabels = colnames(data2), vlcex = 2,
                                        caxislabels = NULL, title = NULL, ...){
  radarchart(
    data2, axistype = 1,
    # Customize the polygon
    pcol = color, pfcol = scales::alpha(color, 0.5), plwd = 2, plty = 1,
    # Customize the grid
    cglcol = "grey", cglty = 1, cglwd = 0.8,
    # Customize the axis
    axislabcol = "grey", 
    # Variable labels
    vlcex = vlcex, vlabels = vlabels,
    caxislabels = caxislabels, title = title, ...
  )
}
op <- par(mar = c(0, 0,0, 0))
create_beautiful_radarchart(rdata1, caxislabels = c(1,2,3,4,5))
par(op)
```
:::
### Lecturer (Guest)

Cluster Innovation Centre, University of Delhi

New Delhi,India

Aug,2016-Apr,2017

- Taught Efficient manufacturing process Production and Operations Management at B. Tech Level.


### English Language Facilitator

AAM Foundation

New Delhi,India

Feb,2013-Aug,2013

- Enabled and encouraged students from underprivileged section of society to learn English.

### Accountant

Government Polytechnic

Jhajjar,India

July,2011-Jan,2012

- Maintain all records like Vouchers, Receipts, Bills, and Payments.

### Treasury Solution Analyst

Bank of America Continuum Solution India Limited

Gurugram,India

Feb,2010-Nov,2010


- Investigate activities of institutions to enforce banking regulations and ensured the legality of transactions and operations or financial solvency.
- Reviewed balance sheets, operating income and expense accounts, and loan documentation to confirm institution assets and liabilities.
- Complete loan applications, including credit analyses and summaries of loan requests, and submitted to loan department for approval.



Workshops {data-icon=users}
--------------------------------------------------------------------------------

### Statistical Techniques for Data Analysis 

Department of Physics, Dr. B.R. Ambedkar National Institute of Technology

Jalandhar,India

22/11/2021-26/11/2021


::: aside
**ENGLISH LANGUAGE TEST**
TOEFL
88/120
:::


###  Block Chain

Indian Institute of Information Technology

Dharwad,India

2/11/2020-6/11/2020

### Artificial Intelligence 

Indian  Institute  of  Information Technology and Management

Gwalior,India

23/11/2020-27/11/2020

### Machine Learning in Real Time Applications 

National Institute of Technology ,Warangal

Warangal,India

24/08/2020-28/08/2020

### Advanced Optimization Techniques and hands-on with MATLAB/SCILAB(3 credit course)

Ministry  of  Electronics  and  Information Technology (MeitY), Government of India

New Delhi,India

13/06/2020-24/06/2020


### Data Science

All India Council for Technical Education

New Delhi,India

20/01/2020-24/01/2020

### Method, Techniques & Analysis of Qualitative Research 

National Institute of Food Technology Entrepreneurship and Management

Kundli,India

17/09/2018-19/09/2018

### TEQIP III Advances in Research Methods and Teaching Pedagogy 

Delhi School of Management at Delhi Technological University

New Delhi,India

18/06/2018-29/06/2018

### Statistical Data Analysis using SPSS

National Institute of Food Technology Entrepreneurship and Management

Kundli,India

28/10/2017-29/10/2017

Certificates {data-icon=certificate}
--------------------------------------------------------------------------------

### Linux Basics. SQL Computer Vision Natural Langugage Processing

CloudxLab.

New Delhi,India

2023


Awards{data-icon=award}
--------------------------------------------------------------------------------

### National Eligibility Test

University Grant Commission

New Delhi,India

Dec,2015

### Bharat  Ratna  Mother  Teresa  Gold  Medal  Award for  Individual Contribution in Social Services

Global Economic Progress and Research Association

Chhenai, India

Jun,2018



::: aside
Disclaimer
--------------------------------------------------------------------------------
This resume was made with the R package [**pagedown**](https://github.com/rstudio/pagedown).
Last updated on `r Sys.Date()`.
:::

